Binning Strategies and Related Loss for Large Data

### 2015-03-20 Paper.Rnw
Outline of New Section 5 for loss properties (explored analytically and through simulation)

>>>>

\section{Exploring Properties of Loss}

\begin{itemize}
\item Binning and frequency binning involve choices (standard/random/quantile, origin, binwidth, number of colors) want to make optimal choices given goals of binning.
\item 3 simulated data sets: from bivariate Exponential, Normal, Uniform
\item Since most data recorded to rough resolution we also assess loss when each dataset is rounded to nearest even value.  
\end{itemize}

\subsection{Spatial binning choices}

\begin{itemize}
\item Binning Algorithm: total and net spatial losses are always larger for random binning than standard (analytical proof)
\item Origin: 
  \begin{itemize}
    \item Doesn't much matter for fine resolution data but it does for coarse data.
    \item If recorded to resolution $\alpha$, origin at $x_{(1)} - \alpha/2$ is optimal (analytical proof then demo)
  \end{itemize} 
\item Binwidth: 
  \begin{itemize}
    \item generally smaller $\omega \rightarrow$ smaller $L^s$. 
    \item for fine data any binwidth is fine
    \item for coarse data need binwidths $\omega \ge \alpha$ (show plot with whitespace gaps)
    \item for coarse data binwidths should be scalar multiple of $\alpha$ (show plot with strips)
    \item Does the distribution type matter? 
  \end{itemize}
\end{itemize}

\subsection{Frequency binning choices}

\begin{itemize}
\item Freq Binning Type
  \begin{itemize}
    \item Comparison of standard, log and quantile binning
  \end{itemize}
\end{itemize}

\begin{itemize}
\item Number of Colors:
  \begin{itemize}
    \item Perception driven limitation to 7 or less color bins
    \item As number colors increases, freq loss goes up?
  \end{itemize}
\end{itemize}
